### Load required packages

```{r}
library(dplyr)
library(ggplot2)
library(lme4)
```

### Read in dataset

```{r}
aquamarine = read.delim("Predator_and_prey_body_sizes_in_marine_food_webs_vsn4.txt")
aquamarine
```

### How many representatives from each life stage?

```{r}
aquamarine %>% 
  group_by(Predator.lifestage) %>% 
  tally()
```

### Exploratory plots

#### Larva and juveniles

```{r}
aquamarine %>% 
  filter(Prey.mass.unit == "g", !is.na(Prey.mass), !is.na(Predator.mass)) %>% 
  filter(Predator.lifestage == "juvenile" | Predator.lifestage == "larva") %>% 
  ggplot(aes(x = Predator.mass, y = Prey.mass, colour = Type.of.feeding.interaction)) + geom_point() + facet_wrap(~Predator.lifestage) + theme_classic()
```

#### Adults and juveniles

```{r}
aquamarine %>% 
  filter(Prey.mass.unit == "g", !is.na(Prey.mass), !is.na(Predator.mass)) %>% 
  filter(Predator.lifestage == "juvenile" |Predator.lifestage == "adult") %>% 
  ggplot(aes(x = Predator.mass, y = Prey.mass, colour = Predator.lifestage )) + geom_point() + facet_wrap(~Type.of.feeding.interaction) + theme_classic()
```

#### Juveniles by feeding interaction

```{r}
aquamarine %>% 
  filter(Prey.mass.unit == "g", !is.na(Prey.mass), !is.na(Predator.mass)) %>% 
  filter(Predator.lifestage == "juvenile" ) %>% 
  ggplot(aes(x = Predator.mass, y = Prey.mass, colour = Predator.lifestage )) + geom_point() + facet_wrap(~Type.of.feeding.interaction) +theme_classic()
```

## Modifying  and plotting data

### Predator mass by prey mass, facet by life stage

```{r}
# Predator prey versus prey mass (g) facetted for each life stage
aquamarine %>% 
  filter(Prey.mass.unit == "g", !is.na(Prey.mass), !is.na(Predator.mass)) %>% 
  filter(Predator.lifestage == "adult" | Predator.lifestage == "juvenile" | Predator.lifestage == "larva") %>% 
  ggplot(aes(x = Predator.mass, y = Prey.mass,colour = Type.of.feeding.interaction)) + geom_point() + facet_wrap(~Predator.lifestage) + theme_classic()
```

#### Change Adults into adults

```{r}
aquamarine$Predator.lifestage[aquamarine$Predator.lifestage == "Adult"] <- "adult"
```

#### Removing NAs for life stage, filter for cryptic life stages such as postlarva

```{r}
life_history_data <- aquamarine %>% 
  filter( !is.na(Prey.mass), !is.na(Predator.mass)) %>% 
  filter(Predator.lifestage == "adult" | Predator.lifestage == "juvenile" | Predator.lifestage == "larva")
```

#### Log transform data

```{r}
life_history_data <- life_history_data %>% 
  mutate(Pred_mass_sqrt = sqrt(Predator.mass), Prey_mass_sqrt = sqrt(Prey.mass), Pred_mass_log = log(SI.predator.mass), Prey_mass_log = log(SI.prey.mass)) %>% 
  mutate (Prey_Pred_mass_l = log(SI.prey.mass/SI.predator.mass))
``` 

### Exploratory plots with log transformed data

#### Predator mass vs prey mass faceted by life stage

```{r}
life_history_data %>% 
  filter(Predator.lifestage == "larva") %>% 
  ggplot(aes(x = Pred_mass_log, y = Prey_mass_log, colour = Predator)) +
  geom_point() +
  facet_wrap(~Predator.lifestage) + 
  theme_classic()
```
#### Histogram of juveniles

```{r}
life_history_data %>% 
  filter(Predator.lifestage == "juvenile") %>% 
  ggplot(aes(x= Pred_mass_log, fill = Predator)) + geom_histogram()
```

### Linear model of adults

```{r}
life_history_data_adult <- life_history_data %>% 
  filter(Predator.lifestage == "adult")
adult_lm <- lm(Prey_mass_log ~ Pred_mass_log , data = life_history_data_adult)
summary (adult_lm) 
```

### Linear model of juveniles

```{r}
life_history_data_juvenile <- life_history_data %>% 
  filter(Predator.lifestage == "juvenile")
summary(juvenile_lm)
```

### Linear model of larva

```{r}
life_history_data_larva <- life_history_data %>% 
  filter(Predator.lifestage == "larva")
larva_lm <- lm(Prey_mass_log ~ Pred_mass_log , data = life_history_data_larva)
summary (larva_lm) 
```

### Add linear models to plot

```{r fig.height=6, fig.width = 10}
life_history_data %>% 
  ggplot(aes(x = Pred_mass_log, y = Prey_mass_log, colour = Predator.lifestage)) +
  geom_point(alpha= 0.1) + geom_abline(slope = 0.3064, intercept = -0.924, colour = "red") +
  geom_abline(slope = 0.742443, intercept = -7.265227 , colour = "green")+ 
  geom_abline(slope =  0.39010 , intercept = -12.06584  , colour = "blue") +
  theme_classic() + labs(y="log(Prey mass) (kg)", x = "log(Predator mass) (kg)")
```

### Basic LM

```{r}
data_lm <- lm(Prey_mass_log ~ Pred_mass_log , data = life_history_data)
summary(data_lm) 
```

### Basic predator prey plots

```{r fig.height=6, fig.width = 10}
life_history_data %>% 
  ggplot(aes(x = Pred_mass_log, y = Prey_mass_log)) +
  geom_point(alpha= 0.1) + geom_abline(slope = 0.936, intercept = -6.426, colour = "black") +
  theme_classic() + labs(y="log(Prey mass) (kg)", x = "log(Predator mass) (kg)")

life_history_data %>% 
  ggplot(aes(x = Pred_mass_log, y = Prey_mass_log, colour = Geographic.location)) +
  geom_point(alpha= 0.1) +theme_classic() + labs( x = "log(Predator mass) (kg) ", y = "log(Prey mass) (kg)")

life_history_data %>% 
  ggplot(aes(x = Pred_mass_log, y = Prey_mass_log, colour = Type.of.feeding.interaction)) +
  geom_point(alpha= 0.1) +theme_classic()
```

###  Basic linear model of interaction

```{r}
feeding_lm <- lm(Prey_mass_log ~ Pred_mass_log*Predator.lifestage , data = life_history_data)
summary(feeding_lm) 
anova(feeding_lm)
```

### Chi square test of interaction

```{r}
chisq.test(life_history_data$Predator.lifestage, life_history_data$Type.of.feeding.interaction)
```

### Bar plot of interaction

```{r}
life_history_data %>% 
  group_by(Predator.lifestage, Type.of.feeding.interaction) %>% 
  ggplot(aes(x= Predator.lifestage, fill = Type.of.feeding.interaction)) + geom_bar() + facet_wrap(~Type.of.feeding.interaction) +theme_classic() + labs(x = "Predator Lifestage")
```

### Random effects model accounting for geographic location

```{r}
feeding_lmer2 <- lmer(Prey_mass_log ~ Pred_mass_log*Predator.lifestage  + (1|Geographic.location) , data = life_history_data)
summary(feeding_lmer2) 
```

### Site plot

```{r}
life_history_data %>% 
  ggplot(aes(x = Pred_mass_log, y = Prey_mass_log, colour = Geographic.location)) +
  geom_point(alpha= 0.5) + 
  theme_classic() + theme(legend.position = "bottom")
```

## Statisitcs and plotting

### Normality of data

```{r}
library(ggplot2)
library(gridExtra)
p1 <- ggplot(life_history_data, aes(Pred_mass_log)) + geom_histogram(fill = "white", colour = "grey30")
p2 <- ggplot(life_history_data, aes(Prey_mass_l)) + geom_histogram(fill = "white", colour = "grey30")
p3 <- ggplot(life_history_data, aes(Prey_Pred_mass_l)) + geom_histogram(bins = 50, fill = "black", colour = "grey30") +theme_classic() 
grid.arrange(p1, p2, p3, ncol =3)

hist(life_history_data$Prey_Pred_mass, w =5)
```

### Normality of adults to use in sample

```{r}
# There are so many data points that need to draw random samples to use in shapiro test (max capacity is 5000)

Adult_sample1 <- life_history_data_adult %>% 
  sample_n(5000, replace = FALSE) 
shapiro.test(Adult_sample1$Pred_mass_log)

Adult_sample2 <- life_history_data_adult %>% 
  sample_n(5000, replace = FALSE) 
shapiro.test(Adult_sample2$Pred_mass_log)

Adult_sample3 <- life_history_data_adult %>% 
  sample_n(5000, replace = FALSE) 
shapiro.test(Adult_sample3$Pred_mass_log)

Adult_sample4 <- life_history_data_adult %>% 
  sample_n(5000, replace = FALSE) 
shapiro.test(Adult_sample4$Pred_mass_log)

Adult_sample5 <- life_history_data_adult %>% 
  sample_n(5000, replace = FALSE) 
shapiro.test(Adult_sample5$Pred_mass_log)

Adult_sample6 <- life_history_data_adult %>% 
  sample_n(5000, replace = FALSE) 
shapiro.test(Adult_sample6$Pred_mass_log)

Adult_sample6 <- life_history_data_adult %>% 
  sample_n(5000, replace = FALSE) 
shapiro.test(Adult_sample6$Prey_mass_log)

Adult_sample7 <- life_history_data_adult %>% 
  sample_n(5000, replace = FALSE) 
shapiro.test(Adult_sample7$Prey_mass_log)

Adult_sample8 <- life_history_data_adult %>% 
  sample_n(5000, replace = FALSE) 
shapiro.test(Adult_sample8$Prey_mass_log)

Adult_sample9 <- life_history_data_adult %>% 
  sample_n(5000, replace = FALSE) 
shapiro.test(Adult_sample9$Prey_mass_log)

Adult_sample10 <- life_history_data_adult %>% 
  sample_n(5000, replace = FALSE) 
shapiro.test(Adult_sample10$Prey_mass_log)
```
### Normality of juveniles to use in sample

```{r}
Juve_sample1 <- life_history_data_juvenile %>%  #significant
  sample_n(5000, replace = FALSE)
shapiro.test(Juve_sample1$Pred_mass_log)

Juve_sample2 <- life_history_data_juvenile %>%  # significant
  sample_n(5000, replace = FALSE)
shapiro.test(Juve_sample2$Pred_mass_log)

Juve_sample3 <- life_history_data_juvenile %>%  # significant
  sample_n(5000, replace = FALSE)
shapiro.test(Juve_sample3$Pred_mass_log)

Juve_sample4 <- life_history_data_juvenile %>%  # significant
  sample_n(5000, replace = FALSE)
shapiro.test(Juve_sample4$Pred_mass_log)

Juve_sample5 <- life_history_data_juvenile %>%  # significant
  sample_n(5000, replace = FALSE)
shapiro.test(Juve_sample5$Pred_mass_log)

Juve_sample6 <- life_history_data_juvenile %>%  #significant
  sample_n(5000, replace = FALSE)
shapiro.test(Juve_sample6$Prey_mass_log)

Juve_sample7 <- life_history_data_juvenile %>%  #significant
  sample_n(5000, replace = FALSE)
shapiro.test(Juve_sample7$Prey_mass_log)

Juve_sample8 <- life_history_data_juvenile %>%  #significant
  sample_n(5000, replace = FALSE)
shapiro.test(Juve_sample8$Prey_mass_log)

Juve_sample9 <- life_history_data_juvenile %>%  #significant
  sample_n(5000, replace = FALSE)
shapiro.test(Juve_sample9$Prey_mass_log)

Juve_sample10 <- life_history_data_juvenile %>%  #significant
  sample_n(5000, replace = FALSE)
shapiro.test(Juve_sample10$Prey_mass_log)
```

### Normality of larva

```{r}
shapiro.test(life_history_data_larva$Pred_mass_log)
shapiro.test(life_history_data_larva$Prey_mass_log)
```
